### 2024-10-24 manuscript.tex
Minor edits

SO radiation biases have been relatively large and systematic compared to the
rest of the globe since at least CMIP3 \citep{trenberth2010}, and the SO SW CRE
bias is still positive in eight analysed CMIP6 models analysed by
\cite{schuddeboom2021} over high-latitude SO, whereas over low-latitude SO it
tends to be more neutral or negative in some models. Too much absorbed SW
radiation over the SO was also identified in the GSRM SCREAM
\cite{caldwell2021}. Compensating biases are possible, such as the `too few too
bright' cloud bias, characterised by too small cloud fraction and too large
cloud albedo \citep{wall2017,kuma2020}, previously described by
\cite{webb2001}, \cite{weare2004}, \cite{zhang2005}, \cite{karlsson2008},
\cite{nam2012}, \cite{klein2013}, and \cite{bender2017} in other regions and
models. That is, a model maintains a resonable SW radiation balance by
reflecting too much SW radiation by cloudy sky but has too little cloudy sky
area overall. A study by \cite{konsta2022} showed that this type bias is still
present in six analysed CMIP6 models in tropical marine clouds, using the
GCM-Oriented Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation
(CALIPSO) Cloud Product [CALIPSO--GOCCP; \cite{chepfer2010}] and Polarization
\& Anisotropy of Reflectances for Atmospheric Sciences coupled with
Observations from a Lidar [PARASOL; \cite{lier2008}] as a reference. They
suggest improper simulation of subgrid-scale cloud heterogeneity as a cause.
Compensating cloud biases in the Australian Community Climate and Earth System
Simulator (ACCESS) – Atmosphere-only model version 2 (AM2) over the SO were
analysed by \cite{fiddes2022} and \cite{fiddes2024}.  \cite{possner2022} showed
that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction
on the order of 30\% [relative to the Moderate Resolution Imaging
Spectroradiometer (MODIS)] and overestimates downwelling TOA SW radiation on
the order of 10 Wm$^\mathrm{-2}$ in  [relative to the Clouds and the Earth’s
Radiant Energy System (CERES)] in the highest model resolution run (2.5 km).
\cite{zhao2022} reported a similar SW radiation bias in five analysed CMIP6
models over high-latitude SO and the total cloud fraction underestimation on
the order of 10\% over the entire 40--60°S SO. Recently, \cite{ramadoss2024}
analysed 48 hours of km-scale ICON limited area model NWP simulation over a
SO region adjacent to Tasmania agaist the Clouds, Aerosols, Precipitation,
Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN)
voyage cloud and precipitation observations. They found the ICON cloud optical
thickness underestimated relative to Himawari‐8 satellite observations, but also
large differences in cloud top phase.

>>>>

SO radiation biases have been relatively large and systematic compared to the
rest of the globe since at least CMIP3 \citep{trenberth2010}, and the SO SW
cloud radiative effect (CRE) bias is still positive in eight analysed CMIP6
models analysed by \cite{schuddeboom2021} over high-latitude SO, whereas over
low-latitude SO it tends to be more neutral or negative in some models. Too
much absorbed SW radiation over the SO was also identified in the GSRM SCREAM
\cite{caldwell2021}. Compensating biases are possible, such as the `too few too
bright' cloud bias, characterised by too small cloud fraction and too large
cloud albedo \citep{wall2017,kuma2020}, previously described by
\cite{webb2001}, \cite{weare2004}, \cite{zhang2005}, \cite{karlsson2008},
\cite{nam2012}, \cite{klein2013}, and \cite{bender2017} in other regions and
models. That is, a model maintains a resonable SW radiation balance by
reflecting too much SW radiation by cloudy sky but has too little cloudy sky
area overall. A study by \cite{konsta2022} showed that this type bias is still
present in six analysed CMIP6 models in tropical marine clouds, using the
GCM-Oriented Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation
(CALIPSO) Cloud Product [CALIPSO--GOCCP; \cite{chepfer2010}] and Polarization
\& Anisotropy of Reflectances for Atmospheric Sciences coupled with
Observations from a Lidar [PARASOL; \cite{lier2008}] as a reference. They
suggest improper simulation of subgrid-scale cloud heterogeneity as a cause.
Compensating cloud biases in the Australian Community Climate and Earth System
Simulator (ACCESS) – Atmosphere-only model version 2 (AM2) over the SO were
analysed by \cite{fiddes2022} and \cite{fiddes2024}.  \cite{possner2022} showed
that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction
on the order of 30\% [relative to the Moderate Resolution Imaging
Spectroradiometer (MODIS)] and overestimates downwelling TOA SW radiation on
the order of 10 Wm$^\mathrm{-2}$ in  [relative to the Clouds and the Earth’s
Radiant Energy System (CERES)] in the highest model resolution run (2.5 km).
\cite{zhao2022} reported a similar SW radiation bias in five analysed CMIP6
models over high-latitude SO and the total cloud fraction underestimation on
the order of 10\% over the entire 40--60°S SO. Recently, \cite{ramadoss2024}
analysed 48 hours of km-scale ICON limited area model NWP simulation over a SO
region adjacent to Tasmania agaist the Clouds, Aerosols, Precipitation,
Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN)
voyage cloud and precipitation observations. They found the ICON cloud optical
thickness underestimated relative to Himawari‐8 satellite observations, but
also large differences in cloud top phase.
